---
title: "HW10 - SNPData"
author: "Festus Asare Yeboah "
date: "July 30, 2017"
output: md_document
---


### SP500 Finanancail Data Analysis

In this Analysis, we demo how to explore and analyse financial data.We use  the SP500 data set as an  example.In our analysis, we find the log returns of our dataset, create our own function to calculate volatility at different periods of time (look back window) and then use the values  to show volatility for different  index values all in one plot.This is to make comparison easier.


### Getting the data
```{r SNPData,message=FALSE}
#Load the t series package and download the SNPdata
library(tseries)
SNPdata <- get.hist.quote('^gspc',quote="Close")
summary(SNPdata)
```
### Analysis
```{r Analysis}
# Calculating  the log returns, 
SNPret <- log(lag(SNPdata)) - log(SNPdata)

# Calculating volatility
SNPvol <- sd(SNPret) * sqrt(250) * 100


#Creating a user defined function called getVol to calculate volatility at different periods
getVol <- function(d, logrets) {
	var = 0
	lam = 0
	varlist <- c()

	for (r in logrets) {
		lam = lam*(1 - 1/d) + 1
	  var = (1 - 1/lam)*var + (1/lam)*r^2
		varlist <- c(varlist, var)
	}

	sqrt(varlist)
}

```
### Volatility Plot

```{r Volatility}
# Get Volatility at 10,SNPret
volest <- getVol(10,SNPret)

# Get Volatility at 30,SNPret
volest2 <- getVol(30,SNPret)

# Get Volatility at 100,SNPret
volest3 <- getVol(100,SNPret)

# Plot the results
plot(volest,type="l")

# Over lay  the values of volest2 on the same plot  
lines(volest2,type="l",col="red")

#  Over lay  the values  of volest3 on the same plot  
lines(volest3, type = "l", col="blue")
```

